---
title: "Activity patterns"
output: html_notebook
---

Testing code to plot activity by species

Set up project:
```{r}
rm(list=ls())
library(dplyr)
library(tidyverse)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics

```
First, let's finally figure out this activity chart! Need to load the TEAM library 1.7.R to get the functions we will use to make the activity chart
```{r}
source("~/Dropbox/R/Zooniverse_work/Camera_Trapping_Ch5_Work/TEAM library 1.7.R")
```
Now, following the Chapter 5 code, hopefully we can get this work. I think we need the data that came from the species accumulation curve because that has time data associated with the detections. Let's load that data too. 


```{r}
masterDF <- read_csv("~/Dropbox/R/Zooniverse_work/Kate/Data/masterDF_test.csv")
```
Now clean up the data to get rid of the nothing theres, something theres, birds, domestics:
```{r}
dump<-which(masterDF$bin == "NOTHINGHERE" | masterDF$bin == "SOMETHINGHERE" | masterDF$bin == "HUMAN" | masterDF$bin == "GROUSERUFFED" | masterDF$bin == "CROWORRAVEN" | masterDF$bin == "OTHERBIRD" | masterDF$bin == "DOMESTICDOG" | masterDF$bin == "OWL" | masterDF$bin == "BLUEJAY" | masterDF$bin == "TURKEY" | masterDF$bin == "GOOSEWILD")
masterDF<-masterDF[-dump,]
```
Now convert some characters to dates:
```{r}
masterDF$Start.Date<- mdy(masterDF$Start.Date)
masterDF$End.Date<-mdy(masterDF$End.Date)
masterDF$ndays<- difftime(masterDF$End.Date, masterDF$Start.Date , units = c("days"))

masterDF<-masterDF[,2:11] #get rid of the weird X1 column
```

Now work on species activity.


```{r}
Activity<-masterDF
Activity$Sampling.Event<-2020 #adds field needed by TEAM functions
Activity<- Activity[,-(10)] #get rid of round number from DF


Activity$td.photo<-as.POSIXct(Activity$td.photo,format="%Y:%m:%d %H:%M:%S")
Activity$Photo.Date<-mdy(Activity$Photo.Date)
Activity$Photo.Time<-hms(Activity$Photo.Time)
Activity$Photo.Time<-period_to_seconds(Activity$Photo.Time) #converts period to number of seconds; 0 seconds is midnight, 86400 is the number of seconds in a day so no value should be greater than that

activity_24h<-events.hours(Activity) #TEAM function; creates matrix with first column as seconds of the day, remaining columns as species.  Indicates the number of detections at the particular time for each species.
```
Now add a column to Activity that assigns the hour corresponding to each Photo.Time.
```{r}
Activity$Hour<-Activity$Photo.Time/3600
Activity$truncHour<-trunc(Activity$Hour)
```
Now add a "day vs. night" category for making the plot fancier

```{r}
Activity$TOD<-"night"
day<-which(Activity$Hour > 5 & Activity$Hour < 19)
Activity$TOD[day]<-"day"
```


Now let's take a look at the data and see if they make sense.

Test case: What is the distribution of porcupine, deer, gray squirrel and rabbit observations over the course of a day?
Porcupine first:

```{r}
Porky<-Activity %>% filter(bin == "PORCUPINE")
ggplot(Porky, aes(truncHour))+
  geom_histogram(bins = 24)
```
Now compare with the circular plot:
```{r}
porcSum<-Porky %>% group_by(truncHour) %>% summarize(
  NumObs=length(Start.Date))
  

clock<-c(0:24)
    PorcPlot<-clock24.plot(porcSum$NumObs, clock, show.grid = T, lwd = 2, line.col = "blue", cex.lab = 0.5)
    PorcPlot

```
Can I color the "slices" so that b/w 18 and 6 is gray background? (to indicate "night"?)


Can we do this for all species at once?

```{r}
Sum<-Activity %>% group_by(truncHour, bin) %>% summarize(
  NumObs=length(Start.Date))
  
Porc<-filter(Sum, bin == "PORCUPINE")

clock<-c(0:24)
    PorcPlot<-clock24.plot(Porc$NumObs, clock, show.grid = T, lwd = 2, line.col = "blue", cex.lab = 0.5)
    PorcPlot
    
```
So, here are the lessons: 
1). Don't need TEAM library or activity_24hour thing at all. Use the switch to filter the Sum data frame to the appropriate species.
2). A good practice is to go back to the original data and do something you know (like plotting a histogram) to see how the data should look in the circular plot.









