---
title: "Shiny App Forest"
output: html_notebook
---


This R Notebook will contain all the shiny apps broken down by forest. Hoping to make tabs with visual results based on forest name.


First, let's clear the environment and load the shiny package.
```{r}
rm(list = ls())
library(shiny)
library(dplyr)
library(readr)
library(ggplot2)
library(tidyverse)
library(rgdal)
library(leaflet)
library(htmltools)
```

Now let's load the data frame we need. This will tell us the total number of species per forest and how many of each species were detected
```{r}
dataFinal <- read_csv("dataFinal.csv")
```

Subset data to remove "Nothing Here" choice
```{r}
dump<-which(dataFinal$choice == "NOTHINGHERE")
newData<-dataFinal[-dump,]
```


Data for trophic tab
```{r}
mammals<- read_csv("mammals.csv")
mammals<- mammals[,2:16]
```



Data for covariates tab
```{r}
Covariates <- read_csv("Covariates.csv")

Cov_sum<-Covariates %>% group_by(Forest) %>% summarise(
  Water = mean(P_Water50), Mixed = mean(P_Mixed50), Evergreen = mean(P_Evergreen50), Deciduous = mean(P_Deciduous50), Development = mean(P_Development50), Agriculture = mean(P_Agriculture50), Barren = mean(P_Barren50), Shrub = mean(P_Shrub50), Wetland = mean(P_Wetland50), Herbaceous = mean(P_Herb50)
)

require(reshape2)
dat_molten <- melt(Cov_sum,"Forest")
require(ggplot2)

copy<-dat_molten
copy[is.na(copy)] = 0
all_forests<- copy %>% group_by(variable) %>% summarise(
value = mean(value)
)


```

For diversity shiny app
```{r}
#Load the data
Diversity_total <- read_csv("Diversity_total.csv")

#Modify the data to match that from my diversity data in thesis code
Diversity_total$BC<-replace(Diversity_total$BC, is.na(Diversity_total$BC), 0)

#Get rid of season
Diversity_total<- Diversity_total[,-2]


divNew<- Diversity_total %>% pivot_longer(-Diversity_Indices, names_to = "Forest", values_to = "index")

divFinal<- aggregate(divNew[, -c(1:2)], by = list(divNew$Diversity_Indices, divNew$Forest), FUN = mean)

#rename from Group.1 and Group.2 
names(divFinal) <- c("Diversity_Indices", "Forest", "Index")

```

```{r}
#Load shape file 
Forests<-readOGR("Data/Study Forest Locations.shp", layer = "Study Forest Locations")

#Project shape file
Forests_proj<-spTransform(Forests, CRS("+proj=longlat +datum=WGS84"))

#reconfigure data frame
dat_sum<-dataFinal %>% group_by(ForestName, choice) %>% summarise(
  number_det = n()
)

labels<-sprintf( "%s", 
                 Forests$ForestCode) %>% lapply(htmltools::HTML)
```

Combined shiny app into tabs; look for these in the app.R file


