---
title: "Activity patterns"
output: html_notebook
---

Make a Shiny app that shows activity patterns by species

Set up project:
```{r}
rm(list=ls())
library(shiny)
library(dplyr)
library(tidyverse)
library(tidyr)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers
```
First, let's finally figure out this activity chart! Need to load the TEAM library 1.7.R to get the functions we will use to make the activity chart
```{r}
source("~/Dropbox/R/Zooniverse_work/Camera_Trapping_Ch5_Work/TEAM library 1.7.R")
```
Now, following the Chapter 5 code, hopefully we can get this work. I think we need the data that came from the species accumulation curve because that has time data associated with the detections. Let's load that data too. 


```{r}
masterDF <- read_csv("~/Dropbox/R/Zooniverse_work/Kate/Data/masterDF_test.csv")
dump<-which(masterDF$bin == "NOTHINGHERE" | masterDF$bin == "SOMETHINGHERE" | masterDF$bin == "HUMAN" | masterDF$bin == "GROUSERUFFED" | masterDF$bin == "CROWORRAVEN" | masterDF$bin == "OTHERBIRD" | masterDF$bin == "DOMESTICDOG" | masterDF$bin == "OWL" | masterDF$bin == "BLUEJAY" | masterDF$bin == "TURKEY" | masterDF$bin == "GOOSEWILD")
masterDF<-masterDF[-dump,]
masterDF$Start.Date<- mdy(masterDF$Start.Date)
masterDF$End.Date<-mdy(masterDF$End.Date)
masterDF$ndays<- difftime(masterDF$End.Date, masterDF$Start.Date , units = c("days"))

masterDF<-masterDF[,2:11]
```

Now work on the species accumulation
```{r}
SpeciesAcc<-masterDF
SpeciesAcc$Sampling.Event<-2020
SpeciesAcc<- SpeciesAcc[,-(10)] #get rid of round number from DF


SpeciesAcc$td.photo<-as.POSIXct(SpeciesAcc$td.photo,format="%Y:%m:%d %H:%M:%S")
SpeciesAcc$Photo.Date<-mdy(SpeciesAcc$Photo.Date)
SpeciesAcc$Photo.Time<-hms(SpeciesAcc$Photo.Time)
```
And activity
```{r}
specActivity<-SpeciesAcc

specActivity$Photo.Time<-period_to_seconds(specActivity$Photo.Time)

activity_24h<-events.hours(specActivity) #Potential error here since we had some NAs. Reporting seconds not 00:00:00
```
Now go over to app.R to run the shiny app



